SPARQL on the Open, Decentralised Web

### 2016-07-30 dissertation/papersincontext.tex
Link to more in structure
inline citations

This work is a paper entitled ``The necessity of hypermedia RDF and an
approach to achieve it'' that was presented in the First Linked APIs
workshop at the Ninth Extended Semantic Web Conference. I was the sole
author. The reference is \cite{kjernsmo_lapis_2012}.

@@

This work resulted in a paper that was nominated for Best Paper on the
Evaluation track on the International Semantic Web Conference 2013,
entitled ``Introducing Statistical Design of Experiments to SPARQL
Endpoint Evaluation'', which was co-authored with John
S. Tyssedal. The reference is \cite{kjernsmo_doe_intro}.

@@

This work resulted in a workshop paper entitled ``Pushing complexity
down the stack'', presented in the Developers Workshop at the
International Semantic Web Conference, by the lead author Gregory Todd
Williams. The reference is \cite{williamspushing}.

@@

I committed to do this survey after Jürgen Umbrich challenged me to see
if the standards were actually followed, and thus address
Problem~\ref{prob:sanity} before further work to solve practical
caching problems. Rather than just survey the
usage for SPARQL Endpoints, I decided to do it for the breadth of the
Semantic Web. This resulted in a research track paper on the Extended
Semantic Web Conference 2015 entitled ``A Survey of HTTP Caching
Implementations on the Open Semantic Web'' with reference
\cite{kjernsmo_survey_2015} and a technical report
\cite{kjernsmo_add_survey_2015} that elaborates on data reduction
methods and statistical methods.

@@

This direction was motivated by a dissatisfaction with the methodology
used in the literature, specifically benchmarking, to test assertions
of performance. That led to exploration of statistical methods referenced
in Section~\ref{sec:condoe}, and to the organising of the Empirical 2014
Workshop at the Extended Semantic Web Conference (which I was
unfortunately prevented from attending myself). Frustrated by
the slow progress of the last 16 years, and the difficulty in comparing
methods to the more mature natural sciences, I still felt the need to
address Problem~\ref{prob:badphil} and express a philosophical view of 
science, which I did by submitting an
article to the ``Negative or inconclusive results in Semantic Web''
workshop at the Extended Semantic Web Conference 2015. The essay, see
\cite{kjernsmo_noise_2015} was tangential to the Call for Papers, but
the chairs decided to accept it as an interview. With Ruben Verborgh
in the role of the interviewer, we reformulated it as
\cite{kjernsmo_noise_2015_interview}, which was published in the
proceedings and is included in the dissertation. It was performed with
Jacco van Ossenbruggen as the interviewer in front of the
audience. The essay, at
\url{http://folk.uio.no/kjekje/2015/noise-essay.html} is however a
more thorough account.

@@

\section{Unpublished Work on Query Caching}

>>>>

This work is a paper entitled ``The necessity of hypermedia RDF and an
approach to achieve it'' that was presented in the First Linked APIs
workshop at the Ninth Extended Semantic Web Conference. I was the sole
author. The citation is:

\begin{quote}
Kjetil Kjernsmo.
\newblock The necessity of hypermedia rdf and an approach to achieve it.
\newblock In {\em Proceedings of the First Linked APIs workshop at the Ninth
  Extended Semantic Web Conference}, May 2012.
\end{quote}

@@

This work resulted in a paper that was nominated for Best Paper on the
Evaluation track on the International Semantic Web Conference 2013,
entitled ``Introducing Statistical Design of Experiments to SPARQL
Endpoint Evaluation'', which was co-authored with John
S. Tyssedal. The citation is:

\begin{quote}
Kjetil Kjernsmo and John~S. Tyssedal.
\newblock Introducing statistical design of experiments to sparql endpoint
  evaluation.
\newblock In Harith Alani, Lalana Kagal, Achille Fokoue, Paul Groth, Chris
  Biemann, Josiane~Xavier Parreira, Lora Aroyo, Natasha Noy, Chris Welty, and
  Krzysztof Janowicz, editors, {\em The Semantic Web – ISWC 2013}, volume
  8219 of {\em Lecture Notes in Computer Science}, pages 360--375. Springer
  Berlin Heidelberg, 2013.
\end{quote}

@@

This work resulted in a workshop paper entitled ``Pushing complexity
down the stack'', presented in the Developers Workshop at the
International Semantic Web Conference, by the lead author Gregory Todd
Williams. The citation is:

\begin{quote}
Gregory~Todd Williams and Kjetil Kjernsmo.
\newblock Pushing complexity down the stack.
\newblock In {\em Proceedings of the ISWC Developers Workshop 2014}, volume
  1268 of {\em {CEUR} Workshop Proceedings}. CEUR-WS.org, May 2014.
\end{quote}

@@

I committed to do this survey after Jürgen Umbrich challenged me to see
if the standards were actually followed, and thus address
Problem~\ref{prob:sanity} before further work to solve practical
caching problems. Rather than just survey the
usage for SPARQL Endpoints, I decided to do it for the breadth of the
Semantic Web. This resulted in a research track paper on the Extended
Semantic Web Conference 2015 entitled ``A Survey of HTTP Caching
Implementations on the Open Semantic Web'' with citation:

\begin{quote}
Kjetil Kjernsmo.
\newblock A survey of http caching implementations on the open semantic web.
\newblock In Fabien Gandon, Marta Sabou, Harald Sack, Claudia d’Amato,
  Philippe Cudré-Mauroux, and Antoine Zimmermann, editors, {\em The Semantic
  Web. Latest Advances and New Domains}, volume 9088 of {\em Lecture Notes in
  Computer Science}, pages 286--301. Springer International Publishing, 2015.
\end{quote}

and a technical report that elaborates on data reduction
methods and statistical methods with the citation:

\begin{quote}
Kjetil Kjernsmo.
\newblock Addendum to a survey of {HTTP} caching on the {Semantic Web}.
\newblock Technical Report 444, Department of Informatics, University of Oslo,
  March 2015.
\end{quote}

@@

This direction was motivated by a dissatisfaction with the methodology
used in the literature, specifically benchmarking, to test assertions
of performance. That led to exploration of statistical methods referenced
in Section~\ref{sec:condoe}, and to the organising of the Empirical 2014
Workshop at the Extended Semantic Web Conference (which I was
unfortunately prevented from attending myself). Frustrated by
the slow progress of the last 16 years, and the difficulty in comparing
methods to the more mature natural sciences, I still felt the need to
address Problem~\ref{prob:badphil} and express a philosophical view of 
science, which I did by submitting an
article to the ``Negative or inconclusive results in Semantic Web''
workshop at the Extended Semantic Web Conference 2015. The essay, see
\cite{kjernsmo_noise_2015} was tangential to the Call for Papers, but
the chairs decided to accept it as an interview. With Ruben Verborgh
in the role of the interviewer, we reformulated it and it was published in the
proceedings and is included in the dissertation. It was performed with
Jacco van Ossenbruggen as the interviewer in front of the
audience. The essay, at
\url{http://folk.uio.no/kjekje/2015/noise-essay.html} is however a
more thorough account. The citation of the interview is:
\begin{quote}
Kjetil Kjernsmo and Ruben Verborgh.
\newblock How can scientific methods provide guidance for semantic web research
  and development.
\newblock In {\em Workshop on Negative or Inconclusive Results in Semantic Web
  Proceedings}, volume 1435 of {\em {CEUR} Workshop Proceedings}. CEUR-WS.org,
  2015.
\end{quote}

@@

\section{Unpublished Work on Query Caching}\label{sec:unpublished}
